### 2019-01-29 thesis_report/theory.tex
First draft of theory+methods+results

	\subsection{Bandstructure of a typical system}

>>>>

	\subsection{Bandstructure of a typical system}
		In Figure \ref{fig:pientka_bandstructure}, the bandstructure is displayed for the SNS system.
		Note that the gap is lowest at the Rashba/Zeeman split fermi-surface, where the momentum in the x direction equals $k_{F,1}$ or $k_{F,2}$.
		It is at these momenta that the wavefunctions are completely parallel to the translationally invariant direction, causing weak couipling with the superconductors.

		\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.5\columnwidth]{figures/pientka_bandstructure}
		\caption{Bandstructure of a straight SNS system~\cite{pientka_topological_2017}.
		Note that the gap is smallest at $k_{F,1}$ and $k_{F,2}$, which correspond to the two different Fermi momenta.}
		\label{fig:pientka_bandstructure}
		\end{figure}
